Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-05-12 text/paper2/ms.tex
paragraph

The likelihood above is evaluated for each star at all time-steps of the simulation during the marginalization --- that is, we consider all possible unbinding times for all stars because there is no way to independently measure $\tub$ for a given star. Furthermore, the idea of a single-valued unbinding time is not well defined as (1) it depends strongly on the particular definition of ``unbound'' and (2) for debris disrupted on near-circular orbits, the debris may pass close to the progenitor several times. We are effectively modeling the distribution of debris as it comes unbound from the satellite, however the exact shape of this distribution in phase-space will depend on the same complicating factors as above. Our choice of using a Gaussian to model the distribution of debris as it is disrupted is simple and almost certainly wrong, but we have found that the exact shape of this distribution is neither well-defined nor significant for a spherical satellite. For example, we find that changing this distribution to a log-normal distribution does not affect our conclusions.

>>>>

The likelihood above is evaluated for each star at all time-steps of the simulation during the marginalization with a uniform prior over all possible unbinding times (no assumptions are made about the orbital phase dependence of mass-loss). We chose this approach because the phase-space position (and hence time) at which a star becomes unbound from a satellite can only be strictly defined for the case of a spherical satellite orbiting on a circular orbit in a spherical potential. Various authors have chosen to measure mass loss in simulations of satellite disruption on eccentric orbits in non-spherical potentials by either looking at the kinetic energy of the particles relative to the satellite's potential energy \citep{johnston96} or looking at the point at which a star crosses the instantaneous tidal radius \citep{kuepper12}. Neither choice is strictly valid and both have been found useful for representing the mass-loss process. Hence we make the simplest choice of using Gaussians to characterize the phase-space distribution of debris as it makes the transition between being bound and unbound. We find that changing this distribution to a log-normal distribution does not affect our conclusions.
